Inferring disease architecture and predictive ability\\with LDpred2-auto

### 2022-09-29 paper/paper-infer.tex
typos

Here we extend LDpred2-auto to make it a highly reliable method for estimating $h^2$ (global and local), $p$ (also per-variant probability for fine-mapping purposes), and $\alpha$.
So, on top of providing competitive PGS, LDpred2-auto can now provide all these estimates of genetic architecture. 
Moreover, we show how it can now also reliably estimate the predictive ability $r^2$ of PGS it derives, allowing for directly assessing the usefulness of the derived PGS, without needing an independent test set.
An overview of what LDpred2-auto can provide is presented in Figure \ref{fig:overview}.
Finally, we extend the set of HapMap3 variants recommended to use with LDpred2, which enables us to capture around 12\% more SNP heritability and achieve around 6\% more predictive performance $r^2$.
We call this new preferred set of 1,444,196 SNPs HapMap3+.

>>>>

Here we extend LDpred2-auto to make it a highly reliable method for estimating $h^2$ (global and local), $p$ (also per-variant probabilities for fine-mapping purposes), and $\alpha$.
So, on top of providing competitive PGS, LDpred2-auto can now provide all these estimates of genetic architecture. 
Moreover, we show how it can now also reliably estimate the predictive ability $r^2$ of PGS it derives, allowing for directly assessing the usefulness of the derived PGS, without needing an independent test set.
An overview of what LDpred2-auto can provide is presented in Figure \ref{fig:overview}.
Finally, we extend the set of HapMap3 variants recommended to use with LDpred2, which enables us to capture around 12\% more SNP heritability and achieve around 6\% more predictive performance $r^2$.
We call this new preferred set of 1,444,196 SNPs HapMap3+.
